### 2024-05-31 journal/analysis.tex
minor edit

We now bound step complexity in terms of the number of processes $p$, the maximum contention $c\leq p$, and the size of the queue.

>>>>

We now bound step complexity in terms of the number of processes $p$, the maximum contention $c\leq p$, and the size of the queue \rev{(i.e., the number of elements in the queue)}.
